---
title: 'Reproducible Pitch: Simulation App for Amplitude Modulation'
author: "Ravi M.B"
date: "July 7, 2018"
output: ioslides_presentation
---

## Modulation:

Modulation is the process of strengthening the message signal with a carrier signal to transmit the signal over long distances. Here in this shiny app, an Modulation with respect to **Amplitude** is performed. A message signal could be mathematically represented as a sine wave. A message signal or in technlogical terms referred also as "Baseband Signal"
consists of the following components

User Inputs:

- Amplitude measured in Volts(**a**)
- Frequency measured in HZ(**f**)
- Time in seconds(**t**)
- Scripts ui.R and server.R code for the Amplitude Modulation app
is availble at [R code](https://github.com/RaviMohan19/MyAmpModApp)

## R Expressions for server based on the inputs

The following R code are expressions evaluated by the server side of the app 

```{r inputs, echo=TRUE}
    f <- 1000
    a <- 5
    omega <- 2 * 3.14 * f
    t <- seq(0, 60, 1)
    msg <- (a * sin(omega * t))
    # carrier wave added
    car_f <- 1000000 # carrier frequency
    carrier <- (a * sin(2 * 3.14 * 1000000 * t)) # carrier signal
    am_wave <- ((1 + msg) * carrier)
    
```

## Server side simulation

Message simulation by server based on the maximum value of the inputs 

```{r msg_plot, echo=FALSE}
library(ggplot2)
qplot(
      t,
      msg,
      geom = "line",
      xlab = "time in seconds",
      ylab = "Amplitude in volts",
      colour = I("green")
    )

```

## Server side simulation Amplitude Modulated Wave

Server simulates the amplitude modulated wave based on the maximum value of inputs

```{r amp_mod_wave, echo=FALSE}
qplot(
      t,
      am_wave,
      geom = "line",
      xlab = "time in seconds",
      ylab = "Amplitude in volts",
      colour = I("blue")
    )
```